An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-03-10 poly-embed-journal/poly-embed-journal.tex
Pass on examples after meeting

Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
We then give three examples of subsequent works that use our framework to study existing surrogates for proposed target losses or derive calibrated polyhedral surrogates for the proposed target via Theorem~\ref{thm:discrete-loss-poly-embeddable}.

When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem (\S~\ref{sec:winge}, \ref{sec:top-k}).
Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:lovasz-hinge}, \ref{sec:top-k}).
\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}

@@

Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' if no one label is sufficiently likely: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ell^{\alpha}$ when $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
\end{equation}
where $\varphi$ embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$. 
Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
\begin{equation}\label{eq:abstain-link-1}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^\alpha$. \jessie{does it?  do we know $\epsilon$ is small enough for higher $d$?}
Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.

\citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}, and that $\psi$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.

@@

\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular and $\ell^f$ is weighted Hamming loss.
Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
\begin{equation}
	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
\end{equation}
(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
Thus, interestingly, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.

@@

\subsection{Inconsistency of previous top-$k$ losses, constructing a calibrated top-$k$ surrogate via embeddings, and verifying a canonical link}
\label{sec:top-k}
In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
Satisfying all three desiderata simultaneously had not been observed until their work.
The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$, as noted by~\citep{lapin2016loss}, which learns more information than desired and seems to require more samples to converge.\jessie{fact check; cite rates paper?}
\citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
Now consider the class of polyhedral surrogates whose calibration for top-$k$ is unknown~\citep{yang2018consistency,lapin2016loss}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.

@@

\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which they are consistent.
%$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task. \jessiet{Do we even want this sentence?}
\citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf. $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessie{not sure how to say this.  better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the link to be the canonical argmax link $\psi^k$.
\jessie{do we want to drop the table here or nah?}

Moreover, \citeauthor{finocchiaro2022consistenttopk} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
\begin{align}\label{eq:topk-embedding}
L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
\end{align}
While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L^k$ to $\elltopk$, we ideally would like to use the intuitive argmax link function 
$\psi^k(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
\citeauthor{finocchiaro2022consistenttopk} Theorem 4.4 confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon < \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/top-k-L4.pdf}
		\end{minipage}\hfill
		\caption{The properties elicited by previous polyhedral surrogates ($\psi_2, \psi_3, \psi_4$ in \citep[Table 1]{yang2018consistency}, respecitvely) with $n = 3, k = 2$. 
		The dashed lines in each simplex denote $\prop{\elltopk}$, and blue regions represent cells where the top-$k$ elements of $\prop{L}$ are ambiguous, and therefore calibration cannot be guaranteed by the argmax link $\psi^k$.
		In this setting, the third surrogate is calibrated via $\psi^k$ with respect to $\elltopk$, though this does not hold for general $k,n$.
		\jessie{revisit}}
		\label{fig:top-k}
	\end{center}
\end{figure}

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L_{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems. \jessie{do we want the ponit about dogan et al or do we not care?}

\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}
\jessie{do we want $k$ or something else, given the previous section?}

The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
\begin{align*}
\ell^\OP(T)_y &= \sum_{i=1}^{k} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
\end{align*}
%\raf{Jessie, could you check that the newer form is correct?  I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}

The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link. \jessie{want to omit this detail?}
Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{L_{WW}}(p)\}$ for each $T \in \T$, outlined in solid black.
These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ is proposed as a surrogate.
\jessie{do we want more detail or save it for the caption/the top-$k$ seciton above?}
\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}

>>>>

Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as verify consistency for specific surrogate and link pairs.
%The embedding framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
We then give three examples of subsequent works that use our framework to study existing surrogates for proposed target losses or derive calibrated polyhedral surrogates for the proposed target via Theorem~\ref{thm:discrete-loss-poly-embeddable}.

When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
%Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it calibrated for the original problem (\S~\ref{sec:top-k}, \ref{sec:winge}).
Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).
\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s) \jessie{burn?}}

@@

Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{1/2} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{1/2}(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. %: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_{1/2}$ and link $\psi^{1/2}$ which are calibrated for $\ell^{1/2}$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
\end{equation}
where $\varphi$ embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Calibration is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi^{1/2}(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$ and choosing $\psi^{1/2}(u) = \bot$ for all $u$ such that $\bot \in \Psi(u)$. 
(For all $u$ such that $\bot \not \in \Psi(u)$, there is only one choice to link, e.g., $|\Psi(u)| = 1$.)
Hence, our framework can be used to verify the calibration of the prposed link $\psi^{1/2}$. \jessiet{changed this sentence.  Thoughts?}%would have simplified the process of finding such a link, and the corresponding proof of consistency.
To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
\begin{equation}\label{eq:abstain-link-1}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^{1/2}$. \jessie{does it?  do we know $\epsilon$ is small enough for higher $d$?}
Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.

Thinking of the abstain loss $\ell^{1/2}$ as a binary structured prediction problem, \citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}. %, and that $\psi^{1/2}$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.

@@

\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular (e.g., $f$ is a weighted Hamming loss).
Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
\begin{equation}
	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
\end{equation}
(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
Thus, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.

@@

\subsection{Inconsistency of previous top-$k$ losses, constructing a calibrated top-$k$ surrogate via embeddings, and verifying a canonical link}
\label{sec:top-k}
In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and upon realizing outcome $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
Satisfying all three desiderata simultaneously had not been observed until the work of~\citet{finocchiaro2022consistenttopk}.
The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$.
\citet{lapin2016loss} observes that this approach learns more information than desired and often requires more samples
% for surrogate regret to approach target regret
~\citep{frongillo2021surrogate}.\jessiet{right?}
\citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
Now consider the class of polyhedral surrogates whose calibration for top-$k$ prediction is unknown~\citep{yang2018consistency,lapin2016loss,lapin2018analysis}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.

@@

\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which previously proposed polyhedral surrogates are consistent.
%$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task. \jessiet{Do we even want this sentence?}
\citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf. $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessiet{not sure how to say this.  better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the canonical argmax link $\psi^k$.
\jessie{do we want to drop the table here or nah?}
Each of the examined surrogates embeds a discrete loss which can be viewed as a variant of the top-$k$ problem, allowing for varying levels of weight on the outcomes or predictions of sets smaller than $k$ elements.
For example, one of the surrogates $L^{(4)}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y}_{[i]})\right)_+$ is minimized in expectation by predicting the set of labels which are ``likely enough,'' up to $k$ labels.
The loss embedded by $L^{(4)}$ might be preferable to top-$k$ in certain settings: for example, if a search engine chooses $c < k$ web results to display for a query by optimizing $L^{(4)}$, the additional $k-c$ slots may be opened to advertisements.

Moreover, \citeauthor{finocchiaro2022consistenttopk} uses the construction from the proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
\begin{align}\label{eq:topk-embedding}
L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
\end{align}
While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L^k$ to $\elltopk$, we ideally would like to use the intuitive argmax link function 
$\psi^k(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
\citep[Theorem 4.4]{finocchiaro2022consistenttopk} confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon \leq \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
\jessiet{COmmenting out reference to old figure}
%See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
%%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.

%\begin{figure}
%	\begin{center}
%		\begin{minipage}{0.32\linewidth}
%			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
%		\end{minipage}\hfill
%		\begin{minipage}{0.32\linewidth}
%			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
%		\end{minipage}\hfill
%		\begin{minipage}{0.32\linewidth}
%			\includegraphics[width=\linewidth]{tikz/top-k-L4.pdf}
%		\end{minipage}\hfill
%		\caption{The properties elicited by previous polyhedral surrogates ($\psi_2, \psi_3, \psi_4$ in \citep[Table 1]{yang2018consistency}, respecitvely) with $n = 3, k = 2$. 
%		The dashed lines in each simplex denote $\prop{\elltopk}$, and blue regions represent cells where the top-$k$ elements of $\prop{L}$ are ambiguous, and therefore calibration cannot be guaranteed by the argmax link $\psi^k$.
%		In this setting, the third surrogate is calibrated via $\psi^k$ with respect to $\elltopk$, though this does not hold for general $k,n$.
%		\jessie{revisit}}
%		\label{fig:top-k}
%	\end{center}
%\end{figure}

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L_{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
The Weston-Watkins hinge was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}. %, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems. 
\jessie{removing point about dogan et al still advocating for WW to be the default}

\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_s) \mid s \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_s = [n]\}~.
\end{align*}

The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
\begin{align*}
\ell^\OP(T)_y &= \sum_{i=1}^{s} \left(|T_{i}| \cdot \Ind{y \not \in T_{i-1}} \right) -1~.~
\end{align*}
%\raf{Jessie, could you check that the newer form is correct?  I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}\jessie{Confirmed}

The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
%\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link. 
\jessiet{Commented out a sentence above; do we want [a modification] of it included?}

Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{L_{WW}}(p)\}$ for each $T \in \T$, outlined in solid black.
These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ was originally proposed as a surrogate.
\jessie{do we want more detail or save it for the caption/the top-$k$ seciton above?}
\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}
